---
title: "README"
output: github_document
Author: Katharina Rumberger,
        Achim Rumbergerer
---
# Evolution in R

## Introduction
We want to create a simple evolution simulation in R.
We will create a very rudumentary environment, with temperature and food, in which a 'organism' will live and reproduce. The organism reproductive success will depend on the adaptation to the enviromental parameters. 

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(R6)
library(dplyr)
library(ggplot2)

knitr::read_chunk("EvoEnvironment.R")
knitr::read_chunk("EvoOrganism.R")
knitr::read_chunk("EvoOrganismGauss.R")
knitr::read_chunk("gaussie.R")
```

## Create Environment Model Class 

We want to use R6 classes to represent out environment 
```{r evo-env}
```

## Create environment
Up to now there seems to be no way, to create data.frames or matrixes with custom S4 or R6 objects.


```{r make_env_list}
#sample(100, 1, replace = TRUE)
#env2 <- EvoEnvironment$new(sample(40, 1, replace = TRUE), sample(100, 1, replace = TRUE))
EnvList <- list()

for(i in 1:100) {
 EnvList[[i]] <- EvoEnvironment$new(sample(40, 1, replace = TRUE), sample(100, 1, replace = TRUE))
}

```

## Create our first organism
The first organism has growth rate dependent on the temperature and nutrients of the environment.
In this first try, nutrients will not be depleted by the organism
```{r evo-org}
```

## Our first live cycle
### Create list of organism. The length of this list is the same as that of the environment list. 
```{r make_org_list}
OrgList <- list()

for (j in 1:length(EnvList) ) {
  OrgList[[j]] <- EvoOrganism$new(tempOpt = 20, nutrientMin = 20, orgCount = 1)
}
```

### Read the envirnonment data
Read the environment data and let the organism grow
```{r let_it_grow, echo=FALSE, results="hide", message = FALSE, warning=FALSE}
for(kk in 1:1) {
  for (k in 1:length(OrgList)) {
    evoOrg <- OrgList[[k]]
    envl <- EnvList[[k]]
    evoOrg$set_envTemperature(envl$temperature)
    evoOrg$set_envNutrient(envl$nutrients)
    evoOrg$determineGrowthrate()
    evoOrg$determineOrgCount()
  }
  kk <- kk + 1
}
```
### first Evaluation - a frequency distribution of organism counts
```{r org_growth_graph, echo=FALSE, results="hide", message = FALSE, warning=FALSE}
x3 <- lapply(OrgList, function(x){return(x$orgCount) })
x4 <- unlist(x3)
qplot(x4, geom="histogram", xlab = 'number of organismis in one environment', main = 'Organism Growth', binwidth = 0.7, fill=I("blue"), col=I("grey"),) + theme(plot.title = element_text(hjust = 0.5))

```
## Evolution with temperature Gauss function 
``` {r gauss-function}
```
## EvoOrganism using this gaussian function to calculate growth rate
``` {r evo-org-gauss}
```
### Create list of our 'gaussian' organism. The length of this list is the same as that of the environment list. 
```{r make_gaussian_org_list}
OrgListGauss <- list()

for (j in 1:length(EnvList) ) {
  OrgListGauss[[j]] <- EvoOrganismGauss$new(tempOpt = 20, nutrientMin = 20, orgCount = 1)
}
```
### Gaussian growth
```{r let_it_grow_guassian, echo=FALSE, results="hide", message = FALSE, warning=FALSE}
for(kk in 1:1) {
  for (k in 1:length(OrgListGauss)) {
    evoOrgGauss <- OrgListGauss[[k]]
    envl <- EnvList[[k]]
    evoOrgGauss$set_envTemperature(envl$temperature)
    evoOrgGauss$set_envNutrient(envl$nutrients)
    evoOrgGauss$determineGrowthrate()
    evoOrgGauss$determineOrgCount()
  }
  kk <- kk + 1
}
```
### first Evaluation - a frequency distribution of gaussian organism counts
```{r gaussian_org_growth_graph, echo=FALSE, results="hide", message = FALSE, warning=FALSE}
x3gauss <- lapply(OrgListGauss, function(x){return(x$orgCount) })
x4gauss <- unlist(x3gauss)
qplot(x4gauss, geom="histogram", xlab = 'number of organisms in one environment', main = 'Gauss Organism Growth', binwidth = 0.7, fill=I("blue"), col=I("grey"),) + theme(plot.title = element_text(hjust = 0.5))

```